---
title: "bsc_s1_preprocess"
output: html_document
---

```{r,include=FALSE}
detachAllPackages <- function() {

  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:datasets","package:methods","package:base")

  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]

  package.list <- setdiff(package.list,basic.packages)

  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)

}

detachAllPackages()
```

```{r setup, include=FALSE}
library(tidyverse)

repo_url <- "https://raw.githubusercontent.com/deanbaltiansky/broken-social-contract/main/study-1/data/"

df_deid <- readr::read_csv(paste0(repo_url,"df_raw_deid.csv"), show_col_types = FALSE)
county_data <- readr::read_csv(paste0(repo_url,"county_data.csv"), show_col_types = FALSE)
bsc_cosinesimilarities <- readr::read_csv(paste0(repo_url,"bsc_cosinesimilarities.csv"), show_col_types = FALSE)
```

remove ineligible participants

```{r}
#keep only those who finished
df_bsc <- df_deid %>% 
  filter(Finished == 1) %>% 
  filter(Progress == 100)
```

Put NA's where necessary

```{r}
df_bsc <- df_bsc %>% 
  mutate(income = ifelse(income == "Prefer not to answer",NA,income))
```

define income and edu as factors

```{r}
df_bsc <- df_bsc %>% 
  mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000")),
         edu = factor(edu,c("noHS",
                            "GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD")))
```

add continuous income and edu vars

```{r}
df_bsc <- df_bsc %>% 
  mutate(income_num = as.numeric(income),
         edu_num = as.numeric(edu))
```

ethnicity

```{r}
df_bsc <- df_bsc %>% 
  mutate(hispanic = ifelse(race_2 == "Hispanic, Latino, or Spanish origin",1,0))
```

fix race

```{r}
df_bsc <- df_bsc %>% 
  mutate_at(vars(race_1:race_8),function(x){as.character(x)}) %>% 
  mutate_at(vars(race_1:race_8),function(x){replace_na(x,"")}) %>% 
  mutate(race_num_1 = ifelse(race_1 != "",1,0),
         race_num_3 = ifelse(race_3 != "",1,0),
         race_num_4 = ifelse(race_4 != "",1,0),
         race_num_5 = ifelse(race_5 != "",1,0),
         race_num_6 = ifelse(race_6 != "",1,0),
         race_num_7 = ifelse(race_7 != "",1,0),
         race_num_8 = ifelse(race_8 != "",1,0),
         race_num = race_num_1 + race_num_3 + race_num_4 + race_num_5 + race_num_6 + race_num_7 + race_num_8,
         race = ifelse(race_num > 1,"multiracial",paste0(race_1,race_3,race_4,race_5,race_6,race_7,race_8)),
         race = ifelse(race == "",NA,race))
```

gender

```{r}
df_bsc <- df_bsc %>% 
  mutate(man = ifelse(gender == "man",1,0))
```


reverse-score items

```{r}
#antiest_4,SDO_3,SDO_4,SDO_7,SDO_8,TIPI_2,TIPI_6,TIPI_8,TIPI_9,TIPI_10
df_bsc <- df_bsc %>% 
  mutate(antiest_4R = 8 - antiest_4,
         SDO_3R = 8 - SDO_3,
         SDO_4R = 8 - SDO_4,
         SDO_7R = 8 - SDO_7,
         SDO_8R = 8 - SDO_8,
         TIPI_2R = 8 - TIPI_2,
         TIPI_6R = 8 - TIPI_6,
         TIPI_8R = 8 - TIPI_8,
         TIPI_9R = 8 - TIPI_9,
         TIPI_10R = 8 - TIPI_10)
```


create mean scores

```{r}
df_bsc <- df_bsc %>% 
  rowwise() %>% 
  mutate(antiest = mean(c(antiest_1,
                          antiest_2,
                          antiest_3,
                          antiest_4R),na.rm = T),
         trust_deminst = mean(c(trust_congress,
                                trust_gov,
                                trust_courts),na.rm = T),
         trust_natinst = mean(c(trust_media,
                                trust_edu,
                                trust_police,
                                trust_millitary,
                                trust_finance,
                                trust_med),na.rm = T),
         trust_science = mean(c(trust_science_1,
                                trust_science_2,
                                trust_science_3),na.rm = T),
         SDO = mean(c(SDO_1,
                      SDO_2,
                      SDO_3R,
                      SDO_4R,
                      SDO_5,
                      SDO_6,
                      SDO_7R,
                      SDO_8R),na.rm = T),
         TIPI_extra = mean(c(TIPI_1,TIPI_6R),na.rm = T),
         TIPI_agree = mean(c(TIPI_2R,TIPI_7),na.rm = T),
         TIPI_consc = mean(c(TIPI_3,TIPI_8R),na.rm = T),
         TIPI_neuro = mean(c(TIPI_4,TIPI_9R),na.rm = T),
         TIPI_open = mean(c(TIPI_5,TIPI_10R),na.rm = T)) %>% 
  ungroup()
```

check and eligibility

```{r}
df_bsc <- df_bsc %>% 
  mutate(check_2 = ifelse(check != 5 | is.na(check),1,0),
         is_elg = ifelse(check_2 == 1,0,1))
```

order of blocks

```{r}
df_bsc <- df_bsc %>% 
  mutate(block_order = ifelse(FL_33_DO_USPAPER == 1,"paper_first","practice_first"))
```

rename

```{r}
df_bsc <- df_bsc %>% 
  rename(ideo_con = ideo_1,
         ideo_lib = ideo_2,
         ideo_demsoc = ideo_3,
         ideo_lbrtn = ideo_4,
         ideo_prog = ideo_5,
         state = county_1,
         county = county_2)
```

county data

```{r}
df_bsc <- df_bsc %>% 
  left_join(county_data,by = c("state","county"))
```

dummy-code voting intentions

```{r}
df_bsc <- df_bsc %>% 
  mutate(vote_2024_trump = ifelse(vote_2024 == "Donald Trump",1,0),
         vote_2024_biden = ifelse(vote_2024 == "Joe Biden",1,0),
         vote_2024_rfkj = ifelse(vote_2024 == "Robert F. Kennedy Jr.",1,0),
         vote_2024_other = ifelse(vote_2024 == "Other",1,0))
```

attach openai similarities (see separate script "bsc_openaiwordembeddings.Rmd")

```{r}
df_bsc <- df_bsc %>% 
  left_join(bsc_cosinesimilarities,by = "PID")
```

reverse simi scores

```{r}
df_bsc <- df_bsc %>% 
  mutate(brokencontract_openai = 1 - simi_openai)
```


take only necessary variables

```{r}
df_bsc <- df_bsc %>% 
  dplyr::select(PID,
                brokencontract_openai,
                simi_openai,
                antiest:TIPI_open,
                vote_tomorrow,
                vote_likely,
                change,
                antiest_1,
                antiest_2,
                antiest_3,
                antiest_4R,
                trust_congress,
                trust_gov,
                trust_courts,
                trust_media,
                trust_edu,
                trust_police,
                trust_millitary,
                trust_finance,
                trust_med,
                trust_science_1,
                trust_science_2,
                trust_science_3,
                SDO_1,
                SDO_2,
                SDO_3R,
                SDO_4R,
                SDO_5,
                SDO_6,
                SDO_7R,
                SDO_8R,
                TIPI_1,TIPI_6R,
                TIPI_2R,TIPI_7,
                TIPI_3,TIPI_8R,
                TIPI_4,TIPI_9R,
                TIPI_5,TIPI_10R,
                check_2,
                is_elg,
                block_order,
                ideo_con:ideo_prog,
                party_id,
                vote_2020,
                vote_2024,
                vote_2024_trump:vote_2024_other,
                income,
                income_num,
                edu,
                edu_num,
                race,
                hispanic,
                age,
                gender,
                man,
                state,
                county,
                county_gini:county_medianincome,
                feedback)
```

write csv

```{r}
write.csv(df_bsc,"~/Google Drive/My Drive/american's dream/for github/broken-social-contract/study-1/data/df_bsc.csv",row.names = F)
```

